Millions of Type Errors

### 2023-04-03 oopsla23/paper.tex
placeholder for file size

\begin{figure}[t]
  \includegraphics{img/row-distribution.pdf}
  \Description{TBD: histogram with about 100 records per hour except for a 600-record spike near the end of Jan 12th.}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California.}
  \label{f:records-per-hour}
\end{figure}

@@

>>>>

\begin{figure}[t]
  \includegraphics{img/row-distribution.pdf}
  \Description{FILL Histogram with approximately 100 records per hour, except for a 600-record spike near the end of Jan 12th.}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California.}
  \label{f:records-per-hour}
\end{figure}

\begin{figure}[t]
  TODO file size distribution: table or bars %% \includegraphics{img/row-distribution.pdf}
  \Description{FILL}
  \caption{Size of analyzed code: number of files, number of lines , and lines in edit region}
  \label{f:analysis-size}
\end{figure}

@@

\subsection{Code Too Complex}

The (example) code is NEVER too complex.

\subsection{TBD}
